Income Disparity and Its Influence on Higher Education Affordability and Access

### 2024-02-19 starter_folder-main 4/paper/college_tuiton_income_inequality.qmd
added some references

R was the language and environment used for this reproduction, alongside different packages such as ggplot2, readxl, dplyr, tidyr, knitr packages.

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-public_data
#| tbl-cap: Public Four Year College Data

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-private_data
#| tbl-cap: Private Four Year College Data

>>>>

R [@citeR] was the language and environment used for this reproduction, with different packages such as tidyverse [@tidyverse], ggplot2 [@ggplot2], readxl [@readxl], dplyr [@dplyr], tidyr [@tidyr], knitr [@knitr] packages.

@@

```{r}
#| label: tbl-public_data
#| tbl-cap: Public Four Year College Data
#| warning: false
#| message: false
#| echo: false

@@

```{r}
#| label: tbl-private_data
#| tbl-cap: Private Four Year College Data
#| warning: false
#| message: false
#| echo: false
